---
title: "Dummy example of network smoothing"
author: "Tyler J Moss"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    fig_caption: yes
vignette: >
  %\VignetteIndexEntry{"Dummy example of network smoothing"}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

This vignette will demonstrate the use of the netPropagate function using dummy networks and data.

## Vignette Info

Note the various macros within the `vignette` setion of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold', fig.cap = "Some random plots."}
plot(1:10, pch =21, bg = colors()[sample(1:500, 10)])
plot(rnorm(10), pch =21, bg = colors()[sample(1:500, 10)])
```

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
